### 2009-09-10 doc/manuals/chelonia/arc-storage-manual.tex
Moved Chelonia documents around
renaming arc_storage_cli to chelonia

{\raggedleft NORDUGRID-XXXXXXX-NN\par}

@@

Now it is time to set up the prototype client tool to access the system. It is currently called \verb!arc_storage_cli! and it is by default installed to \verb!/usr/local/bin!. The CLI tool needs to be told where it can find the user credentials, and a URL of a Bartender service. The Bartender service is the front-end of the storage system. This can be specified either by environment variables, or by a configuration file called \verb!~/.arc/client.xml!. Create the following \verb!client.xml! file:

@@

Now you can use the \verb!arc_storage_cli! to access your local deployment. Try to do a `list' on the root collection (`/'):

\begin{verbatim}
$ arc_storage_cli
Usage:
  arc_storage_cli <method> [<arguments>]
Supported methods:
  stat - get detailed information about an entry
  makeCollection | make | mkdir - create a collection
  unmakeCollection | unmake | rmdir - remove an empty collection
  list | ls - list the content of a collection
  move | mv - move entries within the namespace
  putFile | put - upload a file
  getFile | get - download a file
  delFile | del | rm - remove a file
  modify | mod - modify metadata
  policy | pol - modify access policy rules
  unlink - remove a link to an entry from a collection without removing the entry itself
  credentialsDelegation | cre - delegate credentials for using gateway
  removeCredentials | rem - remove previously delegated credentials
Without arguments, each method prints its own help.

$ arc_storage_cli list
Usage: list <LN> [<LN> ...]

$ arc_storage_cli list /
- Calling the Bartender's list method...
[2009-03-19 18:37:12] [Arc.Loader] [ERROR] [12491/152991544]
    Component tcp.client(tcp) could not be created
[2009-03-19 18:37:12] [Arc.Loader] [ERROR] [12491/152991544]
    Component tls.client(tls) could not be created
[2009-03-19 18:37:12] [Arc.Loader] [ERROR] [12491/152991544]
    Component http.client(http) could not be created
[2009-03-19 18:37:12] [Arc.Loader] [ERROR] [12491/152991544]
    Component soap.client(soap) could not be created
ERROR: Wrong status from server.
Maybe wrong URL: 'https://localhost:60000/Bartender'
\end{verbatim}

@@

Without arguments, the \verb!arc_storage_cli! prints the list of available methods. Specifying only a method name prints the syntax of the given method. The \verb!list! method requires Logical Names (LN). In the storage system, every file and collection has a Logical Name, which is a path within the namespace.

@@

\begin{verbatim}
$ arc_storage_cli list /
- Calling the Bartender's list method...
- done in 0.34 seconds.
'/': not found
\end{verbatim}

@@

\begin{verbatim}
$ arc_storage_cli makeCollection /
- Calling the Bartender's makeCollection method...
- done in 0.81 seconds.
Creating collection '/': done

$ arc_storage_cli list /
- Calling the Bartender's list method...
- done in 0.55 seconds.
'/': collection
    empty.
\end{verbatim}

@@

Assume that Chelonia is running and you want to access it with the \verb!arc_storage_cli! client. The \verb!~/.arc/client.xml! is set properly, the contents of the root collection can be listed:

\begin{verbatim}
$ arc_storage_cli list /
- Calling the Bartender's list method...
- done in 0.55 seconds.
'/': collection
    empty.
\end{verbatim}

@@

$ arc_storage_cli put orange /
- The size of the file is 7 bytes
- Calculating md5 checksum...
- done in 0.0003 seconds, md5 checksum is 6aefd2842be62cd470709b27aedc7db7
- Calling the Bartender's putFile method...
- done in 1.26 seconds.
- Got transfer URL: http://localhost:60001/hopi/7fcef91e-ac9c-658d-4def-17d52ba33cfb
- Uploading from 'orange'
    to 'http://localhost:60001/hopi/7fcef91e-ac9c-658d-4def-17d52ba33cfb' with http...
    0 s:        0.0 kB       0.0 kB/s       0.0 kB/s    . . .       
- done in 0.0182 seconds.
'orange' (7 bytes) uploaded as '/orange'.

$ arc_storage_cli list /
- Calling the Bartender's list method...
- done in 0.51 seconds.
'/': collection
  orange              <file>

@@

\begin{verbatim}
$ arc_storage_cli stat /orange
- Calling the Bartender's stat method...
- done in 0.40 seconds.
'/orange': found
  states
    checksumType: md5
    neededReplicas: 1
    size: 7
    checksum: 6aefd2842be62cd470709b27aedc7db7
  entry
    owner: /DC=eu/DC=KnowARC/O=knowarc/CN=billy
    GUID: 12ce831b-eab8-1f47-29f6-19fb85ebf46a
    type: file
  parents
    0/orange: parent
  locations
    https://localhost:60000/Shepherd 3e9ea612-87c0-1e81-58f3-cec6b0b125c1: alive
  timestamps
    created: 1237504821.91
\end{verbatim}

@@

\begin{verbatim}
$ arc_storage_cli get /orange /tmp
- Calling the Bartender's getFile method...
- done in 0.51 seconds.
- Got transfer URL: http://localhost:60001/hopi/521c5869-4c93-8e28-aa3a-03f477f34f63
- Downloading from 'http://localhost:60001/hopi/521c5869-4c93-8e28-aa3a-03f477f34f63'
    to '/tmp/orange' with http...
    0 s:        0.0 kB       0.0 kB/s       0.0 kB/s    . . .       
- done in 1.0071 seconds.
'/orange' (7 bytes) downloaded as '/tmp/orange'.
$ cat /tmp/orange 
orange
\end{verbatim}

@@

\begin{verbatim}
$ arc_storage_cli makeCollection /fruits
- Calling the Bartender's makeCollection method...
- done in 0.79 seconds.
Creating collection '/fruits': done

$ arc_storage_cli makeCollecion /fruits/apple
- Calling the Bartender's makeCollection method...
- done in 0.91 seconds.
Creating collection '/fruits/apple': done

$ arc_storage_cli move /orange /fruits/
- Calling the Bartender's move method...
- done in 0.99 seconds.
Moving '/orange' to '/fruits/': moved

$ arc_storage_cli list /fruits
- Calling the Bartender's list method...
- done in 0.60 seconds.
'/fruits': collection
  orange              <file>
  apple               <collection>
\end{verbatim}

@@

\begin{verbatim}
$ arc_storage_cli rmdir /fruits
- Calling the Bartender's unmakeCollection method...
- done in 0.41 seconds.
Removing collection '/fruits': collection is not empty

$ arc_storage_cli rmdir /fruits/apple
- Calling the Bartender's unmakeCollection method...
- done in 0.89 seconds.
Removing collection '/fruits/apple': removed

$ arc_storage_cli rm /fruits/orange
- Calling the Bartender's delFile method...
- done in 0.89 seconds.
/fruits/orange: deleted

$ arc_storage_cli rmdir /fruits
- Calling the Bartender's unmakeCollection method...
- done in 0.79 seconds.
Removing collection '/fruits': removed
\end{verbatim}

Now, introduce a new user, Penny, into the system. Again, \verb!arc_storage_cli! can be told to use user certificate and key files for this user with modifying the \verb!client.xml! or by specifying the \verb!ARC_CERT_FILE! and \verb!ARC_KEY_FILE! environment variables.

\begin{verbatim}
$ ARC_CERT_FILE=usercert-penny.pem ARC_KEY_FILE=userkey-penny.pem \
arc_storage_cli list /
- Calling the Bartender's list method...
- done in 0.31 seconds.
'/': denied

$ ARC_CERT_FILE=usercert-penny.pem ARC_KEY_FILE=userkey-penny.pem \
arc_storage_cli put /tmp/orange /pennys-orange
- The size of the file is 7 bytes
- Calculating md5 checksum...
- done in 0.0001 seconds, md5 checksum is 6aefd2842be62cd470709b27aedc7db7
- Calling the Bartender's putFile method...
- done in 0.81 seconds.
/pennys-orange: failed to add child to parent

@@

\begin{verbatim}
$ arc_storage_cli pol / change ALL +read +addEntry
- Calling the Bartender's stat method...
- done in 0.30 seconds.
old action list for the user ALL was ''
the new action list of user ALL for LN / will be '+read +addEntry'
- Calling the Bartender's modify method...
- done in 0.50 seconds.
set.
\end{verbatim}

@@

\begin{verbatim}
$ arc_storage_cli pol
Usage: policy <LN> <changeType> <identity> <action list>
  <changeType> could be 'set', 'change' or 'clear'
    'set': sets the action list to the given user overwriting the old one
    'change': modify the current action list with adding and removing actions
    'clear': clear the action list of the given user
  <identity> could be a '<UserDN>' or a 'VOMS:<VO name>'
  <action list> is a list actions prefixed with '+' or '-'
    e.g. '+read +addEntry -delete'
    possible actions:
        read addEntry removeEntry delete
        modifyPolicy modifyStates modifyMetadata
\end{verbatim}

@@

\begin{verbatim}
$ ARC_CERT_FILE=usercert-penny.pem ARC_KEY_FILE=userkey-penny.pem \
arc_storage_cli put /tmp/orange /pennys-orange
- The size of the file is 7 bytes
- Calculating md5 checksum...
- done in 0.0001 seconds, md5 checksum is 6aefd2842be62cd470709b27aedc7db7
- Calling the Bartender's putFile method...
- done in 1.18 seconds.
- Got transfer URL: http://localhost:60001/hopi/4145891d-0e4c-b6bd-e4d6-dc80554b9d35
- Uploading from '/tmp/orange'
    to 'http://localhost:60001/hopi/4145891d-0e4c-b6bd-e4d6-dc80554b9d35' with http...
    1 s:        0.0 kB       0.0 kB/s       0.0 kB/s    . . .       
- done in 1.0071 seconds.
'/tmp/orange' (7 bytes) uploaded as '/pennys-orange'.
\end{verbatim}

@@

\begin{verbatim}
$ ARC_CERT_FILE=usercert-penny.pem ARC_KEY_FILE=userkey-penny.pem \
arc_storage_cli pol /pennys-orange change /DC=eu/DC=KnowARC/O=knowarc/CN=billy +read
- Calling the Bartender's stat method...
- done in 0.41 seconds.
old action list for the user /DC=eu/DC=KnowARC/O=knowarc/CN=billy was ''
the new action list of user /DC=eu/DC=KnowARC/O=knowarc/CN=billy for LN /pennys-orange
    will be '+read'
- Calling the Bartender's modify method...
- done in 0.59 seconds.
set.

$ arc_storage_cli stat /pennys-orange
- Calling the Bartender's stat method...
- done in 0.43 seconds.
'/pennys-orange': found
  locations
    https://localhost:60000/Shepherd 1cc3b115-2350-8334-d206-a7b891912c00: alive
  states
    checksumType: md5
    neededReplicas: 1
    size: 7
    checksum: 6aefd2842be62cd470709b27aedc7db7
  parents
    0/pennys-orange: parent
  timestamps
    created: 1237509633.17
  policy
    /DC=eu/DC=KnowARC/O=knowarc/CN=billy: +read
  entry
    owner: /DC=eu/DC=KnowARC/O=knowarc/CN=penny
    GUID: 0e6a4c9a-d4e7-e0dc-e083-16b83d460d82
    type: file
\end{verbatim}

@@

\begin{verbatim}
$ arc_storage_cli get /pennys-orange /tmp
- Calling the Bartender's getFile method...
- done in 0.50 seconds.
- Got transfer URL: http://localhost:60001/hopi/c16d7e12-42b0-7882-c09e-1cac31dbdbcd
- Downloading from 'http://localhost:60001/hopi/c16d7e12-42b0-7882-c09e-1cac31dbdbcd'
    to '/tmp/pennys-orange' with http...
    0 s:        0.0 kB       0.0 kB/s       0.0 kB/s    . . .       
- done in 1.0065 seconds.
'/pennys-orange' (7 bytes) downloaded as '/tmp/pennys-orange'.
$ cat /tmp/pennys-orange 
orange
\end{verbatim}

@@

\begin{verbatim}
$ ARC_NEEDED_REPLICAS=2 arc_storage_cli put orange /new-orange
- The size of the file is 7 bytes
- Calculating md5 checksum...
- done in 0.0001 seconds, md5 checksum is 6aefd2842be62cd470709b27aedc7db7
- Calling the Bartender's putFile method...
- done in 1.11 seconds.
- Got transfer URL: http://localhost:60001/hopi/0ad54182-7618-a2af-c490-dea7c4d6fc31
- Uploading from 'orange' to
    'http://localhost:60001/hopi/0ad54182-7618-a2af-c490-dea7c4d6fc31' with http...
    1 s:        0.0 kB       0.0 kB/s       0.0 kB/s    . . .       
- done in 1.0057 seconds.
'orange' (7 bytes) uploaded as '/new-orange'.

$ arc_storage_cli stat /new-orange
- Calling the Bartender's stat method...
- done in 0.40 seconds.
'/new-orange': found
  states
    checksumType: md5
    neededReplicas: 2
    size: 7
    checksum: 6aefd2842be62cd470709b27aedc7db7
  entry
    owner: /DC=eu/DC=KnowARC/O=knowarc/CN=billy
    GUID: 4e673e28-4769-50af-f02e-d7a67632f87a
    type: file
  parents
    0/new-orange: parent
  locations
    https://localhost:60000/Shepherd 4aacd276-653c-3ca5-c1a2-78a876c129c9: alive
  timestamps
    created: 1237509989.43

@@

\begin{verbatim}
$ arc_storage_cli modify /new-orange set states neededReplicas 1
- Calling the Bartender's modify method...
- done in 0.63 seconds.
set

$ arc_storage_cli stat /new-orange | grep neededReplicas
    neededReplicas: 1
\end{verbatim}

It should be noted that the current version of the \verb!arc_storage_cli! tool does not support recursive methods or working with multiple files at once.

@@

\begin{verbatim}
$ arc_storage_cli list /
- Calling the Bartender's list method...
- done in 0.31 seconds.
'/': not found

$ arc_storage_cli makeCollection /
- Calling the Bartender's makeCollection method...
- done in 0.63 seconds.
Creating collection '/': done

$ arc_storage_cli list /
- Calling the Bartender's list method...
- done in 0.50 seconds.
'/': collection
    empty.
\end{verbatim}

@@

\begin{verbatim}
$ ARC_NEEDED_REPLICAS=2 arc_storage_cli put orange /
- The size of the file is 7 bytes
- Calculating md5 checksum...
- done in 0.0005 seconds, md5 checksum is 6aefd2842be62cd470709b27aedc7db7
- Calling the Bartender's putFile method...
- done in 1.10 seconds.
- Got transfer URL: http://storage:60001/hopi/139dc57d-8c12-c188-a4a6-973449553811
- Uploading from 'orange'
    to 'http://storage:60001/hopi/139dc57d-8c12-c188-a4a6-973449553811' with http...
    1 s:        0.0 kB       0.0 kB/s       0.0 kB/s    . . .       
- done in 1.0090 seconds.
'orange' (7 bytes) uploaded as '/orange'.

$ arc_storage_cli stat /orange
- Calling the Bartender's stat method...
- done in 0.41 seconds.
'/orange': found
  states
    checksumType: md5
    neededReplicas: 2
    size: 7
    checksum: 6aefd2842be62cd470709b27aedc7db7
  entry
    owner: /DC=eu/DC=KnowARC/O=knowarc/CN=billy
    GUID: 3fdad88a-944f-79c5-4f23-c5b3d3bc981e
    type: file
  parents
    0/orange: parent
  locations
    https://storage:60000/Shepherd 0b46f53c-419d-ce4e-181a-ec95d16dcc95: alive
  timestamps
    created: 1237519441.96
\end{verbatim}

@@

\begin{verbatim}
$ arc_storage_cli stat /orange
- Calling the Bartender's stat method...
- done in 0.41 seconds.
'/orange': found
  states
    checksumType: md5
    neededReplicas: 2
    size: 7
    checksum: 6aefd2842be62cd470709b27aedc7db7
  entry
    owner: /DC=eu/DC=KnowARC/O=knowarc/CN=billy
    GUID: 24b442eb-ab1a-680e-1f79-4c20479d3ea9
    type: file
  parents
    0/orange: parent
  locations
    https://storage:60000/Shepherd 315d59d3-50cd-1a10-02e6-8e6a528473c3: alive
    https://storage2:60006/Shepherd c1334c09-5d3d-983b-2081-87fe60d4764a: alive
  timestamps
    created: 1237519828.4
\end{verbatim}

@@

\begin{verbatim}
$ arc_storage_cli get /orange /tmp/orange1
- Calling the Bartender's getFile method...
- done in 0.50 seconds.
- Got transfer URL: http://storage:60001/hopi/de0d951f-7379-1ce4-0813-48a384c11982
- Downloading from 'http://storage:60001/hopi/de0d951f-7379-1ce4-0813-48a384c11982'
    to '/tmp/orange1' with http...
    0 s:        0.0 kB       0.0 kB/s       0.0 kB/s    . . .       
- done in 1.0060 seconds.
'/orange' (7 bytes) downloaded as '/tmp/orange1'.

$ arc_storage_cli get /orange /tmp/orange2
- Calling the Bartender's getFile method...
- done in 0.51 seconds.
- Got transfer URL: https://storage2:60006/byteio/52b6bffa-4812-03a5-93a1-834e38077ac5
- Downloading from 'https://storage2:60006/byteio/52b6bffa-4812-03a5-93a1-834e38077ac5'
    to '/tmp/orange2' with byteio...
- done in 0.2822 seconds.
'/orange' (7 bytes) downloaded as '/tmp/orange2'.
\end{verbatim}

@@

\begin{verbatim}
$ arc_storage_cli stat /orange
  locations
    https://storage:60000/Shepherd 315d59d3-50cd-1a10-02e6-8e6a528473c3: alive
    https://storage2:60006/Shepherd c1334c09-5d3d-983b-2081-87fe60d4764a: alive
\end{verbatim}

@@

\begin{verbatim}
$ arc_storage_cli stat /orange
  locations
    https://storage:60000/Shepherd 315d59d3-50cd-1a10-02e6-8e6a528473c3: alive
    https://storage2:60006/Shepherd c1334c09-5d3d-983b-2081-87fe60d4764a: offline

$ arc_storage_cli stat /orange
  locations
    https://storage:60000/Shepherd 315d59d3-50cd-1a10-02e6-8e6a528473c3: alive
    https://storage2:60006/Shepherd c1334c09-5d3d-983b-2081-87fe60d4764a: offline
    https://storage3:60010/Shepherd 421aa939-81fa-5cd9-7c2f-2d5f99a98be1: creating

>>>>

{\raggedleft NORDUGRID-MANUAL-10\par}

@@

Now it is time to set up the prototype client tool to access the system. It is called \verb!chelonia! and it is by default installed to \verb!/usr/local/bin!. The CLI tool needs to be told where it can find the user credentials, and a URL of a Bartender service. The Bartender service is the front-end of the storage system. This can be specified either by environment variables, or by a configuration file called \verb!~/.arc/client.xml!. Create the following \verb!client.xml! file:

@@

Now you can use the tool \verb!chelonia! to access your local deployment. Try to do a `list' on the root collection (`/'):

\begin{verbatim}
$ chelonia
Usage:
  chelonia <method> [<arguments>]
Supported methods:
  stat - get detailed information about an entry
  makeCollection | make | mkdir - create a collection
  unmakeCollection | unmake | rmdir - remove an empty collection
  list | ls - list the content of a collection
  move | mv - move entries within the namespace
  putFile | put - upload a file
  getFile | get - download a file
  delFile | del | rm - remove a file
  modify | mod - modify metadata
  policy | pol - modify access policy rules
  unlink - remove a link to an entry from a collection without removing the entry itself
  credentialsDelegation | cre - delegate credentials for using gateway
  removeCredentials | rem - remove previously delegated credentials
Without arguments, each method prints its own help.

$ chelonia list
Usage: list <LN> [<LN> ...]

$ chelonia list /
- Calling the Bartender's list method...
[2009-03-19 18:37:12] [Arc.Loader] [ERROR] [12491/152991544]
    Component tcp.client(tcp) could not be created
[2009-03-19 18:37:12] [Arc.Loader] [ERROR] [12491/152991544]
    Component tls.client(tls) could not be created
[2009-03-19 18:37:12] [Arc.Loader] [ERROR] [12491/152991544]
    Component http.client(http) could not be created
[2009-03-19 18:37:12] [Arc.Loader] [ERROR] [12491/152991544]
    Component soap.client(soap) could not be created
ERROR: Wrong status from server.
Maybe wrong URL: 'https://localhost:60000/Bartender'
\end{verbatim}

@@

Without arguments, the \verb!chelonia! tool prints the list of available methods. Specifying only a method name prints the syntax of the given method. The \verb!list! method requires Logical Names (LN). In the storage system, every file and collection has a Logical Name, which is a path within the namespace.

@@

\begin{verbatim}
$ chelonia list /
- Calling the Bartender's list method...
- done in 0.34 seconds.
'/': not found
\end{verbatim}

@@

\begin{verbatim}
$ chelonia makeCollection /
- Calling the Bartender's makeCollection method...
- done in 0.81 seconds.
Creating collection '/': done

$ chelonia list /
- Calling the Bartender's list method...
- done in 0.55 seconds.
'/': collection
    empty.
\end{verbatim}

@@

Assume that Chelonia is running and you want to access it with the \verb!chelonia! tool. The \verb!~/.arc/client.xml! is set properly, the contents of the root collection can be listed:

\begin{verbatim}
$ chelonia list /
- Calling the Bartender's list method...
- done in 0.55 seconds.
'/': collection
    empty.
\end{verbatim}

@@

$ chelonia put orange /
- The size of the file is 7 bytes
- Calculating md5 checksum...
- done in 0.0003 seconds, md5 checksum is 6aefd2842be62cd470709b27aedc7db7
- Calling the Bartender's putFile method...
- done in 1.26 seconds.
- Got transfer URL: http://localhost:60001/hopi/7fcef91e-ac9c-658d-4def-17d52ba33cfb
- Uploading from 'orange'
    to 'http://localhost:60001/hopi/7fcef91e-ac9c-658d-4def-17d52ba33cfb' with http...
    0 s:        0.0 kB       0.0 kB/s       0.0 kB/s    . . .       
- done in 0.0182 seconds.
'orange' (7 bytes) uploaded as '/orange'.

$ chelonia list /
- Calling the Bartender's list method...
- done in 0.51 seconds.
'/': collection
  orange              <file>

@@

\begin{verbatim}
$ chelonia stat /orange
- Calling the Bartender's stat method...
- done in 0.40 seconds.
'/orange': found
  states
    checksumType: md5
    neededReplicas: 1
    size: 7
    checksum: 6aefd2842be62cd470709b27aedc7db7
  entry
    owner: /DC=eu/DC=KnowARC/O=knowarc/CN=billy
    GUID: 12ce831b-eab8-1f47-29f6-19fb85ebf46a
    type: file
  parents
    0/orange: parent
  locations
    https://localhost:60000/Shepherd 3e9ea612-87c0-1e81-58f3-cec6b0b125c1: alive
  timestamps
    created: 1237504821.91
\end{verbatim}

@@

\begin{verbatim}
$ chelonia get /orange /tmp
- Calling the Bartender's getFile method...
- done in 0.51 seconds.
- Got transfer URL: http://localhost:60001/hopi/521c5869-4c93-8e28-aa3a-03f477f34f63
- Downloading from 'http://localhost:60001/hopi/521c5869-4c93-8e28-aa3a-03f477f34f63'
    to '/tmp/orange' with http...
    0 s:        0.0 kB       0.0 kB/s       0.0 kB/s    . . .       
- done in 1.0071 seconds.
'/orange' (7 bytes) downloaded as '/tmp/orange'.
$ cat /tmp/orange 
orange
\end{verbatim}

@@

\begin{verbatim}
$ chelonia makeCollection /fruits
- Calling the Bartender's makeCollection method...
- done in 0.79 seconds.
Creating collection '/fruits': done

$ chelonia makeCollecion /fruits/apple
- Calling the Bartender's makeCollection method...
- done in 0.91 seconds.
Creating collection '/fruits/apple': done

$ chelonia move /orange /fruits/
- Calling the Bartender's move method...
- done in 0.99 seconds.
Moving '/orange' to '/fruits/': moved

$ chelonia list /fruits
- Calling the Bartender's list method...
- done in 0.60 seconds.
'/fruits': collection
  orange              <file>
  apple               <collection>
\end{verbatim}

@@

\begin{verbatim}
$ chelonia rmdir /fruits
- Calling the Bartender's unmakeCollection method...
- done in 0.41 seconds.
Removing collection '/fruits': collection is not empty

$ chelonia rmdir /fruits/apple
- Calling the Bartender's unmakeCollection method...
- done in 0.89 seconds.
Removing collection '/fruits/apple': removed

$ chelonia rm /fruits/orange
- Calling the Bartender's delFile method...
- done in 0.89 seconds.
/fruits/orange: deleted

$ chelonia rmdir /fruits
- Calling the Bartender's unmakeCollection method...
- done in 0.79 seconds.
Removing collection '/fruits': removed
\end{verbatim}

Now, introduce a new user, Penny, into the system. Again, \verb!chelonia! can be told to use user certificate and key files for this user with modifying the \verb!client.xml! or by specifying the \verb!ARC_CERT_FILE! and \verb!ARC_KEY_FILE! environment variables.

\begin{verbatim}
$ ARC_CERT_FILE=usercert-penny.pem ARC_KEY_FILE=userkey-penny.pem \
chelonia list /
- Calling the Bartender's list method...
- done in 0.31 seconds.
'/': denied

$ ARC_CERT_FILE=usercert-penny.pem ARC_KEY_FILE=userkey-penny.pem \
chelonia put /tmp/orange /pennys-orange
- The size of the file is 7 bytes
- Calculating md5 checksum...
- done in 0.0001 seconds, md5 checksum is 6aefd2842be62cd470709b27aedc7db7
- Calling the Bartender's putFile method...
- done in 0.81 seconds.
/pennys-orange: failed to add child to parent

@@

\begin{verbatim}
$ chelonia pol / change ALL +read +addEntry
- Calling the Bartender's stat method...
- done in 0.30 seconds.
old action list for the user ALL was ''
the new action list of user ALL for LN / will be '+read +addEntry'
- Calling the Bartender's modify method...
- done in 0.50 seconds.
set.
\end{verbatim}

@@

\begin{verbatim}
$ chelonia pol
Usage: policy <LN> <changeType> <identity> <action list>
  <changeType> could be 'set', 'change' or 'clear'
    'set': sets the action list to the given user overwriting the old one
    'change': modify the current action list with adding and removing actions
    'clear': clear the action list of the given user
  <identity> could be a '<UserDN>' or a 'VOMS:<VO name>'
  <action list> is a list actions prefixed with '+' or '-'
    e.g. '+read +addEntry -delete'
    possible actions:
        read addEntry removeEntry delete
        modifyPolicy modifyStates modifyMetadata
\end{verbatim}

@@

\begin{verbatim}
$ ARC_CERT_FILE=usercert-penny.pem ARC_KEY_FILE=userkey-penny.pem \
chelonia put /tmp/orange /pennys-orange
- The size of the file is 7 bytes
- Calculating md5 checksum...
- done in 0.0001 seconds, md5 checksum is 6aefd2842be62cd470709b27aedc7db7
- Calling the Bartender's putFile method...
- done in 1.18 seconds.
- Got transfer URL: http://localhost:60001/hopi/4145891d-0e4c-b6bd-e4d6-dc80554b9d35
- Uploading from '/tmp/orange'
    to 'http://localhost:60001/hopi/4145891d-0e4c-b6bd-e4d6-dc80554b9d35' with http...
    1 s:        0.0 kB       0.0 kB/s       0.0 kB/s    . . .       
- done in 1.0071 seconds.
'/tmp/orange' (7 bytes) uploaded as '/pennys-orange'.
\end{verbatim}

@@

\begin{verbatim}
$ ARC_CERT_FILE=usercert-penny.pem ARC_KEY_FILE=userkey-penny.pem \
chelonia pol /pennys-orange change /DC=eu/DC=KnowARC/O=knowarc/CN=billy +read
- Calling the Bartender's stat method...
- done in 0.41 seconds.
old action list for the user /DC=eu/DC=KnowARC/O=knowarc/CN=billy was ''
the new action list of user /DC=eu/DC=KnowARC/O=knowarc/CN=billy for LN /pennys-orange
    will be '+read'
- Calling the Bartender's modify method...
- done in 0.59 seconds.
set.

$ chelonia stat /pennys-orange
- Calling the Bartender's stat method...
- done in 0.43 seconds.
'/pennys-orange': found
  locations
    https://localhost:60000/Shepherd 1cc3b115-2350-8334-d206-a7b891912c00: alive
  states
    checksumType: md5
    neededReplicas: 1
    size: 7
    checksum: 6aefd2842be62cd470709b27aedc7db7
  parents
    0/pennys-orange: parent
  timestamps
    created: 1237509633.17
  policy
    /DC=eu/DC=KnowARC/O=knowarc/CN=billy: +read
  entry
    owner: /DC=eu/DC=KnowARC/O=knowarc/CN=penny
    GUID: 0e6a4c9a-d4e7-e0dc-e083-16b83d460d82
    type: file
\end{verbatim}

@@

\begin{verbatim}
$ chelonia get /pennys-orange /tmp
- Calling the Bartender's getFile method...
- done in 0.50 seconds.
- Got transfer URL: http://localhost:60001/hopi/c16d7e12-42b0-7882-c09e-1cac31dbdbcd
- Downloading from 'http://localhost:60001/hopi/c16d7e12-42b0-7882-c09e-1cac31dbdbcd'
    to '/tmp/pennys-orange' with http...
    0 s:        0.0 kB       0.0 kB/s       0.0 kB/s    . . .       
- done in 1.0065 seconds.
'/pennys-orange' (7 bytes) downloaded as '/tmp/pennys-orange'.
$ cat /tmp/pennys-orange 
orange
\end{verbatim}

@@

\begin{verbatim}
$ ARC_NEEDED_REPLICAS=2 chelonia put orange /new-orange
- The size of the file is 7 bytes
- Calculating md5 checksum...
- done in 0.0001 seconds, md5 checksum is 6aefd2842be62cd470709b27aedc7db7
- Calling the Bartender's putFile method...
- done in 1.11 seconds.
- Got transfer URL: http://localhost:60001/hopi/0ad54182-7618-a2af-c490-dea7c4d6fc31
- Uploading from 'orange' to
    'http://localhost:60001/hopi/0ad54182-7618-a2af-c490-dea7c4d6fc31' with http...
    1 s:        0.0 kB       0.0 kB/s       0.0 kB/s    . . .       
- done in 1.0057 seconds.
'orange' (7 bytes) uploaded as '/new-orange'.

$ chelonia stat /new-orange
- Calling the Bartender's stat method...
- done in 0.40 seconds.
'/new-orange': found
  states
    checksumType: md5
    neededReplicas: 2
    size: 7
    checksum: 6aefd2842be62cd470709b27aedc7db7
  entry
    owner: /DC=eu/DC=KnowARC/O=knowarc/CN=billy
    GUID: 4e673e28-4769-50af-f02e-d7a67632f87a
    type: file
  parents
    0/new-orange: parent
  locations
    https://localhost:60000/Shepherd 4aacd276-653c-3ca5-c1a2-78a876c129c9: alive
  timestamps
    created: 1237509989.43

@@

\begin{verbatim}
$ chelonia modify /new-orange set states neededReplicas 1
- Calling the Bartender's modify method...
- done in 0.63 seconds.
set

$ chelonia stat /new-orange | grep neededReplicas
    neededReplicas: 1
\end{verbatim}

It should be noted that the current version of the \verb!chelonia! tool does not support recursive methods or working with multiple files at once.

@@

\begin{verbatim}
$ chelonia list /
- Calling the Bartender's list method...
- done in 0.31 seconds.
'/': not found

$ chelonia makeCollection /
- Calling the Bartender's makeCollection method...
- done in 0.63 seconds.
Creating collection '/': done

$ chelonia list /
- Calling the Bartender's list method...
- done in 0.50 seconds.
'/': collection
    empty.
\end{verbatim}

@@

\begin{verbatim}
$ ARC_NEEDED_REPLICAS=2 chelonia put orange /
- The size of the file is 7 bytes
- Calculating md5 checksum...
- done in 0.0005 seconds, md5 checksum is 6aefd2842be62cd470709b27aedc7db7
- Calling the Bartender's putFile method...
- done in 1.10 seconds.
- Got transfer URL: http://storage:60001/hopi/139dc57d-8c12-c188-a4a6-973449553811
- Uploading from 'orange'
    to 'http://storage:60001/hopi/139dc57d-8c12-c188-a4a6-973449553811' with http...
    1 s:        0.0 kB       0.0 kB/s       0.0 kB/s    . . .       
- done in 1.0090 seconds.
'orange' (7 bytes) uploaded as '/orange'.

$ chelonia stat /orange
- Calling the Bartender's stat method...
- done in 0.41 seconds.
'/orange': found
  states
    checksumType: md5
    neededReplicas: 2
    size: 7
    checksum: 6aefd2842be62cd470709b27aedc7db7
  entry
    owner: /DC=eu/DC=KnowARC/O=knowarc/CN=billy
    GUID: 3fdad88a-944f-79c5-4f23-c5b3d3bc981e
    type: file
  parents
    0/orange: parent
  locations
    https://storage:60000/Shepherd 0b46f53c-419d-ce4e-181a-ec95d16dcc95: alive
  timestamps
    created: 1237519441.96
\end{verbatim}

@@

\begin{verbatim}
$ chelonia stat /orange
- Calling the Bartender's stat method...
- done in 0.41 seconds.
'/orange': found
  states
    checksumType: md5
    neededReplicas: 2
    size: 7
    checksum: 6aefd2842be62cd470709b27aedc7db7
  entry
    owner: /DC=eu/DC=KnowARC/O=knowarc/CN=billy
    GUID: 24b442eb-ab1a-680e-1f79-4c20479d3ea9
    type: file
  parents
    0/orange: parent
  locations
    https://storage:60000/Shepherd 315d59d3-50cd-1a10-02e6-8e6a528473c3: alive
    https://storage2:60006/Shepherd c1334c09-5d3d-983b-2081-87fe60d4764a: alive
  timestamps
    created: 1237519828.4
\end{verbatim}

@@

\begin{verbatim}
$ chelonia get /orange /tmp/orange1
- Calling the Bartender's getFile method...
- done in 0.50 seconds.
- Got transfer URL: http://storage:60001/hopi/de0d951f-7379-1ce4-0813-48a384c11982
- Downloading from 'http://storage:60001/hopi/de0d951f-7379-1ce4-0813-48a384c11982'
    to '/tmp/orange1' with http...
    0 s:        0.0 kB       0.0 kB/s       0.0 kB/s    . . .       
- done in 1.0060 seconds.
'/orange' (7 bytes) downloaded as '/tmp/orange1'.

$ chelonia get /orange /tmp/orange2
- Calling the Bartender's getFile method...
- done in 0.51 seconds.
- Got transfer URL: https://storage2:60006/byteio/52b6bffa-4812-03a5-93a1-834e38077ac5
- Downloading from 'https://storage2:60006/byteio/52b6bffa-4812-03a5-93a1-834e38077ac5'
    to '/tmp/orange2' with byteio...
- done in 0.2822 seconds.
'/orange' (7 bytes) downloaded as '/tmp/orange2'.
\end{verbatim}

@@

\begin{verbatim}
$ chelonia stat /orange
  locations
    https://storage:60000/Shepherd 315d59d3-50cd-1a10-02e6-8e6a528473c3: alive
    https://storage2:60006/Shepherd c1334c09-5d3d-983b-2081-87fe60d4764a: alive
\end{verbatim}

@@

\begin{verbatim}
$ chelonia stat /orange
  locations
    https://storage:60000/Shepherd 315d59d3-50cd-1a10-02e6-8e6a528473c3: alive
    https://storage2:60006/Shepherd c1334c09-5d3d-983b-2081-87fe60d4764a: offline

$ chelonia stat /orange
  locations
    https://storage:60000/Shepherd 315d59d3-50cd-1a10-02e6-8e6a528473c3: alive
    https://storage2:60006/Shepherd c1334c09-5d3d-983b-2081-87fe60d4764a: offline
    https://storage3:60010/Shepherd 421aa939-81fa-5cd9-7c2f-2d5f99a98be1: creating
